\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{amsmath}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Ayush Garg} & Email : \href{mailto:ayushg.iitd@gmail.com}{ayushg.iitd@gmail.com}\\
  \href{mailto:mt1180746@maths.iitd.ac.in}{Sophomore at IIT Delhi,Mathematics and Computing}
   & Mobile : +919911545181 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute Of Technology Delhi }{Delhi, India}
      {Bachelor Of Technology in Mathematics And Computing;  \textbf{CGPA: 9.263/10.0}}{2018 -- Present}
    \resumeSubheading
      {Delhi Public School Indirapuram}{Indirapuram, India}
      {Class XII; \textbf{ 96.6\%}}{July 2018}
    \resumeSubheading
      {Delhi Public School Indirapuram}{Indirapuram, India}
      {Class X; \textbf{CGPA: 10.0/10.0}}{July 2016}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Academic Achievements}
  
      \resumeItemListStart
        \resumeItem{Joint Entrance Examination (Mains)}
          {Secured \textbf{All India Rank(AIR) 28 }among \textbf{1.6 million candidates.}}
        \resumeItem{Joint Entrance Examination (Advanced)}
          {Secured \textbf{All India Rank(AIR) 281 }among \textbf{178,000 candidates.}}
        \resumeItem{KVPY}
          {Secured \textbf{All India Rank(AIR) 87 }among \textbf{200,000 candidates} and \textbf{awarded research fellowship by Dept. of Science And Technology, Govt. of India} }
        \resumeItem{IIT Delhi Director's Merit Scholarship Award}
          {Awarded the scholarship for being in the \textbf{Top 7\%} of all students}
        \resumeItem{A2 Certification in German}
          {Selected by the \textbf{German Embassy} to represent \textbf{India} in Germany along with students from \textbf{20 different countries} and thereafter awarded A2 Certification by \textbf{Goethe Institute,Germany.}}
          
        \resumeItem{International Olympiad of Science (iOS)}
          {Secured \textbf{International Rank 1} among \textbf{2,50,000} candidates \textbf{from 13 countries.}}
      \resumeItemListEnd




%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
  \resumeSubheading{Reading Assistant For Visually Impaired(RAVI)}{Prof. Volker Sorge(\textbf{University of Birmingham)}}
      {Research Project under AssisTech, IIT Delhi}{Ongoing}
      \begin{itemize}
          \item Focuses on making textbooks accessible to \textbf{visually impaired readers} using template based approach for augmenting image description.
          \item Used \textbf{pixel analysis} along with \textbf{connected components} algorithms to create bounding boxes and analyse different parts of the object accordingly.
      \end{itemize}
      
     \resumeSubheading{Recursive Descent Parser}{Prof. Subhashis Banerjee}
      {Winter Semester Project}{January 2019- March 2019}
      \begin{itemize}
          \item Implemented symbolic differentiation of polynomial, exponential, logarithmic and trigonometric functions.
          \item Used the shunting yard algorithm along with stacks in Python3 to make the parser efficient.
      \end{itemize}

   \resumeSubheading{OS CPU Job Scheduler}{Prof. Subodh Kumar}
      {Winter Semester Project}{January 2019- March 2019}
      \begin{itemize}
          \item Implemented \textbf{Tries,Red-Black Trees and Heaps} to store information of Projects,Jobs and Users.
          \item Programmed an allotment algorithm, which works on the principle of remaining and required budget.
      \end{itemize}
  \resumeSubheading{Multi Threaded E-Commerce Platform}{Prof. Subodh Kumar}
      {Summer Semester Project}{July 2019- September 2019}
      \begin{itemize}
          \item Implemented an E-Commerce platform using multi threading in Java.
          \item Sellers were assigned priorities and using the producer consumer model, ensured that the sellers with the maximum priorities are able to sell their products first.
      \end{itemize}
      
       \resumeSubheading{Reverse Car Parking Sensor}{Prof. Subrat Kar}
      {Winter Semester Project}{January 2019- March 2019}
      \begin{itemize}
          \item Implemented a comparator mechanism using LM741 AND LM358 ICs that would lead to increasing intensities of light and sound as the sensor came closer to an obstacle.
          \item Tested in the real world as a part of commercialization of projects initiative resulting in a success rate of \textbf{97.41\%}.
      \end{itemize}
        \resumeSubheading{Triangular Mesh Analysis}{Prof. Subodh Kumar}
      {Summer Semester Project}{July 2019- December 2019}
      \begin{itemize}

          \item Analysed a \textbf{topological triangular mesh} for boundaries, no. of connected components by mapping edges of triangles to edges in a graph.
        \item Implemented efficient analysis algorithms \textbf{using traversals and Dijkstra's algorithm} in graphs.
      \end{itemize}
   
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: GraphQL, Javascript, Node.js, C++, Python, Java, SQL, \LaTeX{}}
      \hfill
      \
    }
     \item{
      \textbf{Softwares}{: Swift, AutoDesk Inventor, iMovie, MS Excel}
      \hfill
      \
    }
     \item{
      \textbf{Frameworks}{: XCode, React-Native, Ignite, AWS, Jest, Enzyme, sklearn}
      \hfill
      \
    }
  \resumeSubHeadingListEnd
  \section{Relevant Courses}
  \resumeSubHeadingListStart
    \item
    {  Calculus, Discrete Mathematics, \textbf{Linear Algebra and Applications}, Differential Equations, \textbf{Probability and Stochastic processes}, Real and Complex analysis, \textbf{Data Structures and Algorithms}, Digital Electronics,\textbf{ Analysis and Design of Algorithms}.}
  \resumeSubHeadingListEnd


%-------------------------------------------
\section{Extra Curricular Activities}
    \resumeSubHeadingListStart
    \item{Worked as \textbf{Manager(Tech+Projects)} and currently \textbf{Team Leader, IIT Delhi} at BloodConnect-\textbf{largest youth run organization} in India in the field of voluntary Blood donation.}
    \item{\textbf{Head of Marketing, Tryst'18}(Annual Tech Fest)}
    \item{Mentored and Guided Freshmen as \textbf{Academic Mentor} for their \textbf{Quantum mechanics and Electro dynamics course}.}
    \item{\textbf{Tennis Vice Captain} - Girnar Hostel}
  \resumeSubHeadingListEnd

\end{document}